Yeast RNA-seq 48 sample simulation study

### 2018-03-06 datasets/RNA-Seq/yeast-simulation.Rmd
Use R utils functions instead of system commands

@@

```{r, download}
system("wget https://github.com/bartongroup/profDGE48/raw/master/Preprocessed_data/Snf2_countdata.tar.gz")
system("wget https://github.com/bartongroup/profDGE48/raw/master/Preprocessed_data/WT_countdata.tar.gz")
system("mkdir yeast48-data")
system("tar -xvf WT_countdata.tar.gz -C ./yeast48-data")
system("tar -xvf Snf2_countdata.tar.gz -C ./yeast48-data")
system("rm *.tar.gz")
```

@@

```{r, readin, results='hide', message=FALSE}
files <- dir(path = "./yeast48-data/", pattern = "*.bam.gbgout", full.names = TRUE)
sample_names <- sapply(strsplit(dir(path = "./yeast48-data/", pattern = "*.bam.gbgout"), "_MID"),
                       function(x) x[[1]])

@@

```{r, results='hide', message=FALSE}
rseed <- 225
sampleSize <- 5
nDE <- 0

system("mkdir -p yeast48-results")

if (!file.exists("yeast48-results/null5.rds")){
  null5 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
  saveRDS(null5, file="yeast48-results/null5.rds")
}else{
  null5 <- readRDS(file="yeast48-results/null5.rds")
}

@@

```{r, results='hide', message=FALSE}
rseed <- 837
sampleSize <- 10
nDE <- 0

if (!file.exists("yeast48-results/null10.rds")){
  null10 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
  saveRDS(null10, file="yeast48-results/null10.rds")
}else{
  null10 <- readRDS(file="yeast48-results/null10.rds")
}

@@

```{r, results='hide', message=FALSE}
rseed <- 198
sampleSize <- 5
nDE <- 500

if (!file.exists("yeast48-results/de5.rds")){
  de5 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
  saveRDS(de5, file="yeast48-results/de5.rds")
}else{
  de5 <- readRDS(file="yeast48-results/de5.rds")
}
```

@@

plotsim_average(res5d, met="rejections",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res5d, met="FPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res5d, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE)

@@

```{r, results='hide', message=FALSE}
rseed <- 961
sampleSize <- 10
nDE <- 500

if(!file.exists("yeast48-results/de10.rds")){
  de10 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
  saveRDS(de10, file="yeast48-results/de10.rds")
}else{
  de10 <- readRDS(file="yeast48-results/de10.rds")
}
```

@@

plotsim_average(res10d, met="rejections",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res10d, met="FPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res10d, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE)

>>>>

# set up data / results directories
datdir <- "yeast-data"
resdir <- "yeast-results"
dir.create(datdir, showWarnings = FALSE)
dir.create(resdir, showWarnings = FALSE)

@@

```{r, download}
download.file(url = "https://github.com/bartongroup/profDGE48/raw/master/Preprocessed_data/Snf2_countdata.tar.gz",
              destfile = paste0(datdir, "/Snf2_countdata.tar.gz"))
download.file(url = "https://github.com/bartongroup/profDGE48/raw/master/Preprocessed_data/WT_countdata.tar.gz", 
              destfile = paste0(datdir, "/WT_countdata.tar.gz"))

gunzip(paste0(datdir, "/Snf2_countdata.tar.gz")) 
gunzip(paste0(datdir, "/WT_countdata.tar.gz"))

untar(paste0(datdir, "/Snf2_countdata.tar"), exdir = datdir) 
untar(paste0(datdir, "/WT_countdata.tar"), exdir = datdir)

file.remove(paste0(datdir, "/Snf2_countdata.tar"), 
            paste0(datdir, "/WT_countdata.tar"))
```

@@

```{r, readin, results='hide', message=FALSE}
files <- dir(path = datdir, pattern = "*.bam.gbgout", full.names = TRUE)
sample_names <- sapply(strsplit(dir(path = datdir, pattern = "*.bam.gbgout"), "_MID"),
                       function(x) x[[1]])

@@

```{r, results='hide', message=FALSE}
rseed <- 225
sampleSize <- 5
nDE <- 0
resfile <- paste0(resdir, "/null5.rds")

if (!file.exists(resfile)){
  null5 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
  saveRDS(null5, file=resfile)
}else{
  null5 <- readRDS(file=resfile)
}

@@

```{r, results='hide', message=FALSE}
rseed <- 837
sampleSize <- 10
nDE <- 0
resfile <- paste0(resdir, "/null10.rds")

if (!file.exists(resfile)){
  null10 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
  saveRDS(null10, file=resfile)
}else{
  null10 <- readRDS(file=resfile)
}

@@

```{r, results='hide', message=FALSE}
rseed <- 198
sampleSize <- 5
nDE <- 500
resfile <- paste0(resdir, "/de5.rds")

if (!file.exists(resfile)){
  de5 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
  saveRDS(de5, file=resfile)
}else{
  de5 <- readRDS(file=resfile)
}
```

@@

plotsim_average(res5d, met="rejections",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res5d, met="FDR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res5d, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE)

@@

```{r, results='hide', message=FALSE}
rseed <- 961
sampleSize <- 10
nDE <- 500
resfile <- paste0(resdir, "/de10.rds")

if(!file.exists(resfile)){
  de10 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
  saveRDS(de10, file=resfile)
}else{
  de10 <- readRDS(file=resfile)
}
```

@@

plotsim_average(res10d, met="rejections",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res10d, met="FDR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res10d, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE)
